---
title: "CAET vs Environment"
output: html_document
date: "2024-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
Main_Survey <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Main Survey",
                        check.names = TRUE)

Indicators <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Calculated Indicators",
                        check.names = TRUE)%>%
  select(farm_id, dietary_diversity:pest_score)%>%
  select(-c(inc3,structure, compaction, depth, residues,
            color, water_ret, cover, erosion, invertebrates, microbio))

data <- left_join(Main_Survey,
                         Indicators)

#import functions to use for analysis
source("../functions.R")
```

## Agrobiodiversity

### Gini-Simpson index of diversity for animals

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSIndex_animals",
    ytitle = "Gini-Simpson index of diversity for animals",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSIndex_animals",
    facet = "location_level_one_name",
    ytitle = "Gini-Simpson index of diversity for animals",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "GSIndex_animals")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "GSIndex_animals",
          title = "Gini-Simpson index of diversity for animals" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "GSIndex_animals",
          title = "Gini-Simpson index of diversity for animals")
```

### Gini-Simpson index of diversity for animals

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSIndex_animals",
    ytitle = "Gini-Simpson index of diversity for animals",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSIndex_animals",
    facet = "location_level_one_name",
    ytitle = "Gini-Simpson index of diversity for animals",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "GSIndex_animals")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "GSIndex_animals",
          title = "Gini-Simpson index of diversity for animals" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "GSIndex_animals",
          title = "Gini-Simpson index of diversity for animals")
```

### Gini-Simpson index of diversity for natural vegetation and pollinators

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSI_other",
    ytitle = "Gini-Simpson index of diversity\nfor natural vegetation and pollinators",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GSI_other",
    facet = "location_level_one_name",
    ytitle = "Gini-Simpson index of diversity\nfor natural vegetation and pollinators",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "GSI_other")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "GSI_other",
          title = "Gini-Simpson index of diversity\nfor natural vegetation and pollinators" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "GSI_other",
          title = "Gini-Simpson index of diversity\nfor natural vegetation and pollinators")
```

### Number of species and varieties of crops

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "num_crops_c1",
    ytitle = "Number of species and varieties of crops",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "num_crops_c1",
    facet = "location_level_one_name",
    ytitle = "Number of species and varieties of crops",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "num_crops_c1")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "num_crops_c1",
          title = "Number of species and varieties of crops" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "num_crops_c1",
          title = "Number of species and varieties of crops")
```

### Number of species and breeds of animals

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "num_animals_a1",
    ytitle = "Number of species and breeds of animals",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "num_animals_a1",
    facet = "location_level_one_name",
    ytitle = "Number of species and breeds of animals",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "num_animals_a1")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "num_animals_a1",
          title = "Number of species and breeds of animals" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "num_animals_a1",
          title = "Number of species and breeds of animals")
```

### Livestock Units

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_lsu",
    ytitle = "Livestock Units",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_lsu",
    facet = "location_level_one_name",
    ytitle = "Livestock Units",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "total_lsu")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "total_lsu",
          title = "Livestock Units" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "total_lsu",
          title = "Livestock Units")
```