---
title: "Kenya - CAET vs Food and Nutrition"
output: html_document
date: "2024-02-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
Main_Survey <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Main Survey",
                        check.names = TRUE)

Indicators <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Calculated Indicators",
                        check.names = TRUE)%>%
  select(farm_id, dietary_diversity:pest_score)%>%
  select(-c(inc3,structure, compaction, depth, residues,
            color, water_ret, cover, erosion, invertebrates, microbio))

data <- left_join(Main_Survey,
                         Indicators)

#import functions to use for analysis
source("../functions.R")
```

## Dietary Diversity

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "dietary_diversity",
    ytitle = "Dietary Diversity (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "dietary_diversity",
    facet = "location_level_one_name",
    ytitle = "Dietary Diversity (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### Spearman's rank Correlations

```{r}
correlations_table(indicator = "dietary_diversity")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "dietary_diversity",
          title = "Dietary Diversity")
```

### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "dietary_diversity",
          title = "Dietary Diversity")
```

## Food Insecurity Experience Scale

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "fies_score",
    ytitle = "FIES (Food Insecurity Experience Scale) Score",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "fies_score",
    facet = "location_level_one_name",
    ytitle = "FIES (Food Insecurity Experience Scale) Score",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```




### Spearman's rank Correlations

```{r}
correlations_table(indicator = "fies_score")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "fies_score",
          title = "FIES (Food Insecurity Experience Scale) Score")
```

### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "fies_score",
          title = "FIES (Food Insecurity Experience Scale) Score")
```

## Food Expenditure per person

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "food_exp_capita",
    ytitle = "Food Expenditure per Capita (Kenya Shilling)",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "food_exp_capita",
    facet = "location_level_one_name",
    ytitle = "Food Expenditure per Capita (Kenya Shilling)",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

### Spearman's rank Correlations

```{r}
correlations_table(indicator = "food_exp_capita")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "food_exp_capita",
          title = "Food Expenditure per Capita (Kenya Shilling)")
```

### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "food_exp_capita",
          title = "Food Expenditure per Capita (Kenya Shilling)")
```
