---
title: "CAET vs Pesticides"
output: html_document
date: "2024-02-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)


#read in performance data
source("../readdata.R")

#read in functions for scripts
source("../functions.R")

```

## Exposure to Pesticides

### Quantity of chemical pesticides used

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cpused",
    ytitle = "Quantity of chemical pesticides used",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "coused",
    facet = "location_level_one_name",
    ytitle = "Quantity of chemical pesticides used",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "cpused")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "cpused",
          title = "Quantity of chemical pesticides used" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "cpused",
          title = "Quantity of chemical pesticides used")
```

### Used extremely toxic chemical pesticides

#### Fisher Test

```{r}
indicator_fisher_test("ctox1",
                      "Used extremely toxic pesticides")
```

#### T-test of mean caet score extreme toxicity chemical pesticide use

```{r}
data %>%
    dplyr::select(totscore_caet, ctox1, pro_soils_group) %>%
    dplyr::mutate(pro_soils_group = ifelse(pro_soils_group == 1,
                                            "ProSoils",
                                            "Non-ProSoils")) %>%
    tidyr::nest(data = c(totscore_caet, ctox1)) %>%
    dplyr::mutate(data = purrr::map(data, ~ {
        out <- t.test(.x$totscore_caet ~ .x$ctox1)
        tibble::tibble(
            "No extreme toxicity" = out$estimate[1],
            "Using extremely toxic pesticides" = out$estimate[2],
            Difference = out$estimate[1] - out$estimate[2],
            `t-value` = out$statistic,
            p.value = out$p.value
        )
    })) %>%
    tidyr::unnest(cols = data) %>%
    flextable::flextable() %>%
    flextable::colformat_double(j = 2:5, digits = 1) %>%
    flextable::colformat_double(j = 6, digits = 3) %>%
    flextable::theme_alafoli() %>%
    flextable::bg(part = "all", bg = "white") %>%
    flextable::autofit()
```

### Used moderately toxic chemical pesticides

#### Fisher Test

```{r}
indicator_fisher_test("ctox2",
                      "Used moderately toxic pesticides")
```

#### T-test of mean caet score moderate toxicity chemical pesticide use

```{r}
data %>%
    dplyr::select(totscore_caet, ctox2, pro_soils_group) %>%
    dplyr::mutate(pro_soils_group = ifelse(pro_soils_group == 1,
                                            "ProSoils",
                                            "Non-ProSoils")) %>%
    tidyr::nest(data = c(totscore_caet, ctox2)) %>%
    dplyr::mutate(data = purrr::map(data, ~ {
        out <- t.test(.x$totscore_caet ~ .x$ctox2)
        tibble::tibble(
            "No moderate toxicity" = out$estimate[1],
            "Using moderately toxic pesticides" = out$estimate[2],
            Difference = out$estimate[1] - out$estimate[2],
            `t-value` = out$statistic,
            p.value = out$p.value
        )
    })) %>%
    tidyr::unnest(cols = data) %>%
    flextable::flextable() %>%
    flextable::colformat_double(j = 2:5, digits = 1) %>%
    flextable::colformat_double(j = 6, digits = 3) %>%
    flextable::theme_alafoli() %>%
    flextable::bg(part = "all", bg = "white") %>%
    flextable::autofit()
```

### Used extremely toxic organic pesticides

```{r}
n <- nrow(data%>%filter(otox1=="Yes"))

if(n>0){
indicator_fisher_test("otox2",
                      "Used moderately toxic organic pesticides")
}
```

### Used moderately toxic organic pesticides

#### Fisher Test

```{r}
indicator_fisher_test("otox2",
                      "Used moderately toxic organic pesticides")
```

### Area of use of pesticides - Checmical

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cpused_ha",
    ytitle = "Area of use of pesticides - Checmical",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "coused",
    facet = "location_level_one_name",
    ytitle = "Area of use of pesticides - Checmical",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "cpused_ha")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "cpused_ha",
          title = "Area of use of pesticides - Checmical" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "cpused_ha",
          title = "Area of use of pesticides - Checmical")
```

### Area of use of pesticides - organic

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "coused_ha",
    ytitle = "Area of use of pesticides - organic",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "coused_ha",
    facet = "location_level_one_name",
    ytitle = "Area of use of pesticides - organic",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "coused_ha")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "coused_ha",
          title = "Area of use of pesticides - organic" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "coused_ha",
          title = "Area of use of pesticides - organic")
```

### Number of mitigations strategies

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "mitigation_num",
    ytitle = "Number of mitigations strategies",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "mitigation_num",
    facet = "location_level_one_name",
    ytitle = "Number of mitigations strategies",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "mitigation_num")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "mitigation_num",
          title = "Number of mitigations strategies" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "mitigation_num",
          title = "Number of mitigations strategies")
```

```{r}
# data%>%
#     select(pro_soils_group, mitig1:mitig7)%>%
#     mutate_all(function(x) replace_na(x,0))%>%
#     pivot_longer(mitig1:mitig7, names_to = "Strategy")%>%
#     mutate(Strategy = case_when(
#         Strategy == "mitig1" ~ "Mask",
#         Strategy == "mitig2" ~ "Body Protection",
#         Strategy == "mitig3" ~ "Special Protection",
#         Strategy == "mitig4" ~ "Visible signs of danger after spraying",
#         Strategy == "mitig5" ~ "Community is informed of the danger",
#         Strategy == "mitig6" ~ "Secure disposal of the empty containers after use",
#         Strategy == "mitig7" ~ "Other"
#     ))%>%
#     mutate(pro_soils_group = ifelse(pro_soils_group == 1, "ProSoils", "Non-ProSoils"))%>%
#     group_by(pro_soils_group, Strategy)%>%
#     summarise(perc = mean(value),
#               n = sum(value))%>%
#     mutate(perc_n = paste0(round(perc*100,1), "% (", n, ")"))%>%
#     select(-perc, - n)%>%
#     pivot_wider(names_from = pro_soils_group, values_from = perc_n)%>%
#     flextable()%>%
#     autofit()
```

### Number of ecological pest management practices

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "ecoman_num",
    ytitle = "Number of ecological pest management practices",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "ecoman_num",
    facet = "location_level_one_name",
    ytitle = "Number of ecological pest management practices",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "ecoman_num")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "ecoman_num",
          title = "Number of ecological pest management practices" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "ecoman_num",
          title = "Number of ecological pest management practices")
```

```{r}
# data%>%
#     select(pro_soils_group, ecoman1:ecoman5,ecoman77)%>%
#     mutate_all(function(x) replace_na(x,0))%>%
#     pivot_longer(ecoman1:ecoman77, names_to = "Strategy")%>%
#     mutate(Strategy = case_when(
#         Strategy == "ecoman1" ~ "Cultural control",
#         Strategy == "ecoman2" ~ "Plantation of natural repelling plants",
#         Strategy == "ecoman3" ~ "Use of cover crops to increase biological interactions",
#         Strategy == "ecoman4" ~ "Favor the reproduction of beneficial organisms for biological-control",
#         Strategy == "ecoman5" ~ "Favor biodiversity and spatial diversity within the agroecosystem",
#         Strategy == "ecoman77" ~ "Other",
#     ))%>%
#     mutate(pro_soils_group = ifelse(pro_soils_group == 1, "ProSoils", "Non-ProSoils"))%>%
#     group_by(pro_soils_group, Strategy)%>%
#     summarise(perc = mean(value),
#               n = sum(value))%>%
#     mutate(perc_n = paste0(round(perc*100,1), "% (", n, ")"))%>%
#     select(-perc, - n)%>%
#     pivot_wider(names_from = pro_soils_group, values_from = perc_n)%>%
#     flextable()%>%
#     autofit()
```

### Integrated Pest Management Score (0 - 100%)

#### Overall Scatter

```{r}
 caet_performance_scatter(
     x = "totscore_caet",
     y = "pest_score",
     ytitle = "Integrated Pest Management Score",
     xtitle = "Total CAET Score",
     min = 0,
     max = 100
 )
```

  By Region

```{r}
 caet_performance_scatter(
     x = "totscore_caet",
     y = "pest_score",
     facet = "location_level_one_name",
     ytitle = "Integrated Pest Management Score",
     xtitle = "Total CAET Score",
     min = 0,
     max = 100
 )
```

  Spearman's rank Correlations

```{r}
 correlations_table(indicator = "pest_score")
```

 Test of Mean - ProSoils vs Comparison

```{r}
 mean_test(indicator = "pest_score",
           title = "Integrated Pest Management Score (0 - 100%)" )
```

Test of Median - ProSoils vs Comparison
```{r}
#median_test(indicator = "pest_score",
#           title = "Integrated Pest Management Score (0 - 100%)")
```
