---
title: "CAET vs Soil Health"
output: html_document
date: "2024-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
Main_Survey <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Main Survey",
                        check.names = TRUE)

Indicators <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Calculated Indicators",
                        check.names = TRUE)%>%
  select(farm_id, dietary_diversity:pest_score)%>%
  select(-c(inc3,structure, compaction, depth, residues,
            color, water_ret, cover, erosion, invertebrates, microbio))

data <- left_join(Main_Survey,
                         Indicators)

#import functions to use for analysis
source("../functions.R")
```

## Soil Health

### Soil Structure

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "structure",
    ytitle = "Soil Structure",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "structure",
    facet = "location_level_one_name",
    ytitle = "Soil Structure",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "structure")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "structure",
          title = "Soil Structure" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "structure",
          title = "Soil Structure")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "structure",
                      title = "Soil Structure")
```

### Soil compaction

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "compaction",
    ytitle = "Soil compaction",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "compaction",
    facet = "location_level_one_name",
    ytitle = "Soil compaction",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "compaction")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "compaction",
          title = "Soil compaction" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "compaction",
          title = "Soil compaction")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "compaction",
                      title = "Soil compaction")
```


### Soil depth

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "depth",
    ytitle = "Soil depth",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "depth",
    facet = "location_level_one_name",
    ytitle = "Soil depth",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "depth")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "depth",
          title = "Soil depth" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "depth",
          title = "Soil depth")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "depth",
                      title = "Soil depth")
```


### Soil residues

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "residues",
    ytitle = "Status of residues",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "residues",
    facet = "location_level_one_name",
    ytitle = "Status of residues",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "residues")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "residues",
          title = "Status of residues" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "residues",
          title = "Status of residues")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "residues",
                      title = "Status of residues")
```

### Soil color

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "color",
    ytitle = "Soil color",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "color",
    facet = "location_level_one_name",
    ytitle = "Soil color",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "color")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "color",
          title = "Soil color" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "color",
          title = "Soil color")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "color",
                      title = "Soil color")
```

### Soil water retention

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "water_ret",
    ytitle = "Soil water retention",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "water_ret",
    facet = "location_level_one_name",
    ytitle = "Soil water retention",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "water_ret")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "water_ret",
          title = "Soil water retention" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "water_ret",
          title = "Soil water retention")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "water_ret",
                      title = "Soil water retention")
```

### Soil cover

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cover",
    ytitle = "Soil cover",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cover",
    facet = "location_level_one_name",
    ytitle = "Soil cover",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "cover")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "cover",
          title = "Soil cover" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "cover",
          title = "Soil cover")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "cover",
                      title = "Soil cover")
```

### Soil erosion

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "erosion",
    ytitle = "Soil erosion",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "erosion",
    facet = "location_level_one_name",
    ytitle = "Soil erosion",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "erosion")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "erosion",
          title = "Soil erosion" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "erosion",
          title = "Soil erosion")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "erosion",
                      title = "Soil erosion")
```

### Presence of invertebrates

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "invertebrates",
    ytitle = "Presence of invertebrates",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "invertebrates",
    facet = "location_level_one_name",
    ytitle = "Presence of invertebrates",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "invertebrates")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "invertebrates",
          title = "Presence of invertebrates" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "invertebrates",
          title = "Presence of invertebrates")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "invertebrates",
                      title = "Presence of invertebrates")
```

### Presence of Microbiological activity

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "microbio",
    ytitle = "Presence of Microbiological activity",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "microbio",
    facet = "location_level_one_name",
    ytitle = "Presence of Microbiological activity",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "microbio")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "microbio",
          title = "Presence of Microbiological activity" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "microbio",
          title = "Presence of Microbiological activity")
```

#### Fisher test

```{r}
indicator_fisher_test(indicator = "microbio",
                      title = "Presence of Microbiological activity")
```

### Soil health index

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "soil_health",
    ytitle = "Soil health index",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "soil_health",
    facet = "location_level_one_name",
    ytitle = "Soil health index",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "soil_health")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "soil_health",
          title = "Soil health index" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "soil_health",
          title = "Soil health index")
```

