---
title: "CAET vs Food and Nutrition"
output: html_document
date: "2024-02-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
source("../readdata.R")

#read in functions for scripts
source("../functions.R")

```

## Dietary Diversity

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "dietary_diversity",
    ytitle = "Dietary Diversity (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "dietary_diversity",
    facet = "location_level_one_name",
    ytitle = "Dietary Diversity (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### Spearman's rank Correlations

```{r}
correlations_table(indicator = "dietary_diversity")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "dietary_diversity",
          title = "Dietary Diversity")
```

### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "dietary_diversity",
          title = "Dietary Diversity")
```

## Food Insecurity Experience Scale

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "fies_score",
    ytitle = "FIES (Food Insecurity Experience Scale) Score",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "fies_score",
    facet = "location_level_one_name",
    ytitle = "FIES (Food Insecurity Experience Scale) Score",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```




### Spearman's rank Correlations

```{r}
correlations_table(indicator = "fies_score")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "fies_score",
          title = "FIES (Food Insecurity Experience Scale) Score")
```

### Test of Median - ProSoils vs Comparison

```{r}

## if fies_score (that is not null) has over 50% values at 100, do not do median test
if (sum(data %>% filter(!is.na(fies_score)) %>% pull(fies_score) == 100) / nrow(data) > 0.5) {
  print("Over 50% of values are at 100, median test not performed")
} else {
  median_test(indicator = "fies_score",
              title = "FIES (Food Insecurity Experience Scale) Score")
}

```

## Food Expenditure per person

### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "food_exp_capita",
    ytitle = paste("Food Expenditure per Capita (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "food_exp_capita",
    facet = "location_level_one_name",
    ytitle = paste("Food Expenditure per Capita (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

### Spearman's rank Correlations

```{r}
correlations_table(indicator = "food_exp_capita")
```

### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "food_exp_capita",
          title = paste("Food Expenditure per Capita (", currency, ")"))
```

### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "food_exp_capita",
          title = paste("Food Expenditure per Capita (", currency, ")"))
```
