---
title: "CAET vs Social Indicators"
output: html_document
date: "2024-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
source("../readdata.R")

#read in functions for scripts
source("../functions.R")

```

## Women's Empowerment

### Women Empowerment score A-WEAI

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "AWEAI",
    ytitle = "Women Empowerment score A-WEAI (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "AWEAI",
    facet = "location_level_one_name",
    ytitle = "Women Empowerment score A-WEAI (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "AWEAI")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "AWEAI",
          title = "Women Empowerment score A-WEAI (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "AWEAI",
          title = "Women Empowerment score A-WEAI (0-100%)")
```

### Gender Parity Index

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GPI",
    ytitle = "Gender Parity Index (0-100%)",
    xtitle = "Total CAET Score"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "GPI",
    facet = "location_level_one_name",
    ytitle = "Gender Parity Index (0-100%)",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "GPI")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "GPI",
          title = "Gender Parity Index (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "GPI",
          title = "Gender Parity Index (0-100%)")
```


### Percentage of female adults (15+ yo) in the household working in agriculture

```{r}
janitor::tabyl(data, hh_women, pro_soils_group)%>%
    janitor::adorn_percentages(denominator = "col")%>%
    janitor::adorn_pct_formatting()%>%
    janitor::adorn_ns()%>%
    flextable::flextable()%>%
    flextable::set_header_labels(values = list(
        hh_women = "Number of\nadult women\nin the household",
        `0` = "Non-ProSoils",
        `1` = "ProSoils"
    ))%>%
    flextable::autofit()
```

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_fadult_ag",
    ytitle = "Percentage of female adults (15+ yo) in\nthe household working in agriculture (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_fadult_ag",
    facet = "location_level_one_name",
    ytitle = "Percentage of female adults (15+ yo) in\nthe household working in agriculture (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "pct_fadult_ag")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "pct_fadult_ag",
          title = "Percentage of female adults (15+ yo) in\nthe household working in agriculture (0-100%) (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "pct_fadult_ag",
          title = "Percentage of female adults (15+ yo) in\nthe household working in agriculture (0-100%) (0-100%)")
```

## Youth Empowerment

### Youth Employment score

#### Overall Scatter

Overall Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_employ",
    ytitle = "Youth Employment score (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

Female Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_employ_f",
    ytitle = "Youth Employment score - Female (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

Male Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_employ_m",
    ytitle = "Youth Employment score - Male (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_employ",
    facet = "location_level_one_name",
    ytitle = "Youth Employment score  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "youth_employ")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "youth_employ",
          title = "Youth Employment score (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "youth_employ",
          title = "Youth Employment score (0-100%)")
```


### Youth Emigration score

#### Overall Scatter

Overall Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_emigr",
    ytitle = "Youth Emigration score (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```
Female Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_emigr_f",
    ytitle = "Youth Emigration score - Female (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

Male Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_emigr_m",
    ytitle = "Youth Emigration score - Male (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```


#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_emigr",
    facet = "location_level_one_name",
    ytitle = "Youth Emigration score  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "youth_emigr")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "youth_emigr",
          title = "Youth Emigration score (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "youth_emigr",
          title = "Youth Emigration score (0-100%)")
```

### Overall Youth score

#### Overall Scatter

Overall

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_score",
    ytitle = "Overall Youth score (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```


Female Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_score_f",
    ytitle = "Overall Youth score - Female (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

Male Score

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_score_m",
    ytitle = "Overall Youth score - Male (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```


#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "youth_score",
    facet = "location_level_one_name",
    ytitle = "Overall Youth score  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "youth_score")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "youth_score",
          title = "Overall Youth score (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "youth_score",
          title = "Overall Youth score (0-100%)")
```


### Percentage of youth (15-34 yo) in the household working in agriculture

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_youth_ag",
    ytitle = "Percentage of youth (15-34 yo) in\nthe household working in agriculture (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_youth_ag",
    facet = "location_level_one_name",
    ytitle = "Percentage of youth (15-34 yo) in\nthe household working in agriculture  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "pct_youth_ag")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "pct_youth_ag",
          title = "Percentage of youth (15-34 yo) in\nthe household working in agriculture (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "pct_youth_ag",
          title = "Percentage of youth (15-34 yo) in\nthe household working in agriculture (0-100%)")
```

## Other

### Percentage of children in the household working in agriculture

```{r}
janitor::tabyl(data, hh_children, pro_soils_group)%>%
    janitor::adorn_percentages(denominator = "col")%>%
    janitor::adorn_pct_formatting()%>%
    janitor::adorn_ns()%>%
    flextable::flextable()%>%
    flextable::set_header_labels(values = list(
        hh_children = "Number of\nchidlren (<15)\nin the household",
        `0` = "Non-ProSoils",
        `1` = "ProSoils"
    ))%>%
    flextable::autofit()
```

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_ag_children",
    ytitle = "Percentage of children\nin the household working in agriculture (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_ag_children",
    facet = "location_level_one_name",
    ytitle = "Percentage of children\nin the household working in agriculture  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "pct_ag_children")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "pct_ag_children",
          title = "Percentage of children\nin the household working in agriculture (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "pct_ag_children",
          title = "Percentage of children\nin the household working in agriculture (0-100%)")
```

### Percentage of family in the household working in agriculture

#### Overall Scatter


```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_family_ag",
    ytitle = "Percentage of family\nin the household working in agriculture (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_family_ag",
    facet = "location_level_one_name",
    ytitle = "Percentage of family\nin the household working in agriculture  (0-100%)",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "pct_family_ag")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "pct_family_ag",
          title = "Percentage of family\nin the household working in agriculture (0-100%)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "pct_family_ag",
          title = "Percentage of family\nin the household working in agriculture (0-100%)")
```
