---
title: "CAET vs Economic Indicators"
output: html_document
date: "2024-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)
library(janitor)

#read in performance data
Main_Survey <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Main Survey",
                        check.names = TRUE)

Indicators <- read.xlsx("FILEPATH TO DATA HERE",
                        sheet = "Calculated Indicators",
                        check.names = TRUE)%>%
  select(farm_id, dietary_diversity:pest_score)%>%
  select(-c(inc3,structure, compaction, depth, residues,
            color, water_ret, cover, erosion, invertebrates, microbio))

data <- left_join(Main_Survey,
                         Indicators)

#import functions to use for analysis
source("../functions.R")
```

## Value Added

### Total expenditures for the purchase of seeds, fertilizers, pesticides, machineries

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_expenditures",
    ytitle = "Total expenditures for the purchase of\nseeds, fertilizers, pesticides, machineries",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_expenditures",
    facet = "location_level_one_name",
    ytitle = "Total expenditures for the purchase of\nseeds, fertilizers, pesticides, machineries",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "total_expenditures")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "total_expenditures",
          title = "Total expenditures for the purchase of\nseeds, fertilizers, pesticides, machineries" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "total_expenditures",
          title = "Total expenditures for the purchase of\nseeds, fertilizers, pesticides, machineries")
```

### Value added (Total)

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added",
    ytitle = "Value added (total)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added",
    facet = "location_level_one_name",
    ytitle = "Value added (total)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "value_added")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "value_added",
          title = "Value added (total)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "value_added",
          title = "Value added (total)")
```

### Value added (Per Person)

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_pcapita",
    ytitle = "Value added (Per Person)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_pcapita",
    facet = "location_level_one_name",
    ytitle = "Value added (Per Person)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "value_added_pcapita")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "value_added_pcapita",
          title = "Value added (Per Person)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "value_added_pcapita",
          title = "Value added (Per Person)")
```

### Value added (Per ha)

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_ha",
    ytitle = "Value added (Per ha)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_ha",
    facet = "location_level_one_name",
    ytitle = "Value added (Per ha)",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "value_added_ha")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "value_added_ha",
          title = "Value added (Per ha)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "value_added_ha",
          title = "Value added (Per ha)")
```

### Value added on Gross value of the production (VA/GVP)

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_gvp",
    ytitle = "Value added on Gross value of\nthe production (VA/GVP)",
    xtitle = "Total CAET Score"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "value_added_gvp",
    facet = "location_level_one_name",
    ytitle = "Value added on Gross value of\nthe production (VA/GVP)",
    xtitle = "Total CAET Score"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "value_added_gvp")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "value_added_gvp",
          title = "Value added on Gross value of the production (VA/GVP)" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "value_added_gvp",
          title = "Value added on Gross value of the production (VA/GVP)")
```

## Income

### Crop Sales

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "crop_sales",
    ytitle = "Crop Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "crop_sales",
    facet = "location_level_one_name",
    ytitle = "Crop Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "crop_sales")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "crop_sales",
          title = "Crop Sales" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "crop_sales",
          title = "Crop Sales")
```

### Crop and forestry product Sales

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cfp_sales",
    ytitle = "Crop and forestry product Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "cfp_sales")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "cfp_sales",
          title = "Crop and forestry product Sales" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "cfp_sales",
          title = "Crop and forestry product Sales")
```

### animal Sales

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anim_sales",
    ytitle = "animal Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

##### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anim_sales",
    facet = "location_level_one_name",
    ytitle = "animal Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "anim_sales")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "anim_sales",
          title = "animal Sales" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "anim_sales",
          title = "animal Sales")
```

### animal and livestock product Sales

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anpr_sales",
    ytitle = "animal and livestock product Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### By region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anpr_sales",
    facet = "location_level_one_name",
    ytitle = "animal and livestock product Sales",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "anpr_sales")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "anpr_sales",
          title = "animal and livestock product Sales" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "anpr_sales",
          title = "animal and livestock product Sales")
```

### Revenue derived from other activities

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "acrev",
    ytitle = "Revenue derived from other activities",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "acrev")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "acrev",
          title = "Revenue derived from other activities" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "acrev",
          title = "Revenue derived from other activities")
```

### Cost of Renting Land

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "finance_exp",
    ytitle = "Cost of Renting Land",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "finance_exp")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "finance_exp",
          title = "Cost of Renting Land" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "finance_exp",
          title = "Cost of Renting Land")
```

### Net revenue from agropastoral activities

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "netrev",
    ytitle = "Net revenue from agropastoral activities",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "netrev",
    facet = "location_level_one_name",
    ytitle = "Net revenue from agropastoral activities",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "netrev")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "netrev",
          title = "Net revenue from agropastoral activities" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "netrev",
          title = "Net revenue from agropastoral activities")
```

### % of revenue derived from crops and livestock

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_rev_crop_liv",
    ytitle = "% of revenue derived from crops and livestock",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### By region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "pct_rev_crop_liv",
    facet = "location_level_one_name",
    ytitle = "% of revenue derived from crops and livestock",
    xtitle = "Total CAET Score",
    min = 0,
    max = 100
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "pct_rev_crop_liv")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "pct_rev_crop_liv",
          title = "% of revenue derived from crops and livestock" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "pct_rev_crop_liv",
          title = "% of revenue derived from crops and livestock")
```

### % of people under poverty level

#### Chi-Square Test

```{r}
x <- janitor::tabyl(data, intl_poverty, pro_soils_group)%>%chisq.test()

janitor::tabyl(data%>%mutate(intl_poverty = ifelse(intl_poverty == 1, "Yes", "No")),
               intl_poverty, pro_soils_group) %>%
        janitor::adorn_percentages(denominator = "col") %>%
        janitor::adorn_pct_formatting() %>%
        janitor::adorn_ns() %>%
        flextable::flextable() %>%
        flextable::set_header_labels(values = list(
            intl_poverty = "Living below poverty line?",
            `0` = "Non-ProSoils",
            `1` = "ProSoils"
        )) %>%
        flextable::autofit() %>%
        flextable::theme_alafoli() %>%
        flextable::bg(part = "all", bg = "white") %>%
        flextable::add_footer_lines(values = paste0("Chi2 test - p.value = ", round(x$p.value, 3)))
```

#### T-test of mean caet score by povert status

```{r}
data %>%
    dplyr::select(totscore_caet, intl_poverty, pro_soils_group) %>%
    dplyr::mutate(pro_soils_group = ifelse(pro_soils_group == 1,
                                            "ProSoils",
                                            "Non-ProSoils")) %>%
    tidyr::nest(data = c(totscore_caet, intl_poverty)) %>%
    dplyr::mutate(data = purrr::map(data, ~ {
        out <- t.test(.x$totscore_caet ~ .x$intl_poverty)
        tibble::tibble(
            "Not in Poverty" = out$estimate[1],
            "In Poverty" = out$estimate[2],
            Difference = out$estimate[1] - out$estimate[2],
            `t-value` = out$statistic,
            p.value = out$p.value
        )
    })) %>%
    tidyr::unnest(cols = data) %>%
    flextable::flextable() %>%
    flextable::colformat_double(j = 2:5, digits = 1) %>%
    flextable::colformat_double(j = 6, digits = 3) %>%
    flextable::theme_alafoli() %>%
    flextable::bg(part = "all", bg = "white") %>%
    flextable::autofit()
```

### Depreciation

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "depreciation",
    ytitle = "Depreciation",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### By region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "depreciation",
    facet = "location_level_one_name",
    ytitle = "Depreciation",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "depreciation")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "depreciation",
          title = "Depreciation" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "depreciation",
          title = "Depreciation")
```

### Expenditures for  wages

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "totwage",
    ytitle = "Expenditures for  wages",
    xtitle = "Total CAET Score",
    min = 0,
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "totwage")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "totwage",
          title = "Expenditures for  wages" )
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "totwage",
          title = "Expenditures for  wages")
```

### Qualitative perception of earnings and expenditures

##### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "inc3_inverse",
    ytitle = "Qualitative perception of earnings and expenditures\n
    (1 = Much less income - 5 = Much more)",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "inc3_inverse",
    facet = "location_level_one_name",
    ytitle = "Qualitative perception of earnings and expenditures\n
    (1 = Much less income - 5 = Much more)",
    xtitle = "Total CAET Score",
    min = 1,
    max = 5
)
```


#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "inc3_inverse")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "inc3_inverse",
          title = "Qualitative perception of earnings and expenditures\n
    (1 = Much less income - 5 = Much more)")
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "inc3_inverse",
          title = "Qualitative perception of earnings and expenditures\n
    (1 = Much less income - 5 = Much more)")
```