---
title: "CAET vs Productivity"
output: html_document
date: "2024-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    error = FALSE,
    message = FALSE
)

#renv::restore()

# Load Libraries
library(tidyverse)
library(openxlsx)
library(flextable)
library(fmsb)

#read in performance data
source("../readdata.R")

#read in functions for scripts
source("../functions.R")

```

## Value of crop and forestry products produced

### Crop Value

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "crop_prodval",
    ytitle = paste("Total value of crop production (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "crop_prodval",
    facet = "location_level_one_name",
    ytitle = paste("Total value of crop production (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "crop_prodval")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "crop_prodval",
          title = paste("Total value of crop production (", currency, ")"))
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "crop_prodval",
          title = paste("Total value of crop production (", currency, ")"))
```

### Total value of crop and forestry products

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cfp_prodval",
    ytitle = paste("Total value of crop and forestry products (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "cfp_prodval",
    facet = "location_level_one_name",
    ytitle = paste("Total value of crop and forestry products (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "cfp_prodval")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "cfp_prodval",
          title = paste("Total value of crop and forestry products (", currency, ")"))
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "cfp_prodval",
          title = paste("Total value of crop and forestry products (", currency, ")"))
```

## Value of animal and livestock products produced

### animal Value

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anim_prodval",
    ytitle = paste("Total value of animal production (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anim_prodval",
    facet = "location_level_one_name",
    ytitle = paste("Total value of animal production (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "anim_prodval")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "anim_prodval",
          title = paste("Total value of animal production (", currency, ")"))
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "anim_prodval",
          title = paste("Total value of animal production (", currency, ")"))
```

### Total value of animal and livestock products

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anpr_prodval",
    ytitle = paste("Total value of animal and livestock products (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "anpr_prodval",
    facet = "location_level_one_name",
    ytitle = paste("Total value of animal and livestock products (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "anpr_prodval")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "anpr_prodval",
          title = paste("Total value of animal and livestock products (", currency, ")"))
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "anpr_prodval",
          title = paste("Total value of animal and livestock products (", currency, ")"))
```

## Total value of farm outputs (crops, animals, crop and forestry products, animal products)

### Total Output

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_output",
    ytitle = paste("Total value of farm outputs\n(crops, animals, crop and forestry products, animal products)\n (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "total_output",
    facet = "location_level_one_name",
    ytitle = paste("Total value of farm outputs\n(crops, animals, crop and forestry products, animal products)\n (", currency, ")"),
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "total_output")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "total_output",
          title = paste("Total value of farm outputs\n(crops, animals, crop and forestry products, animal products)\n (", currency, ")"))
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "total_output",
          title = paste("Total value of farm outputs\n(crops, animals, crop and forestry products, animal products)\n (", currency, ")"))
```

## Gross value of the agricultural production (per person / per ha)

### Per person

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "tot_productivity_pers",
    ytitle = "Total productivity per person\ncrops, animals, crop\nand forestry products, animal products",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "tot_productivity_pers",
    facet = "location_level_one_name",
    ytitle = "Total productivity per person\ncrops, animals, crop\nand forestry products, animal products",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "tot_productivity_pers")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "tot_productivity_pers",
          title = "Total productivity per person\ncrops, animals, crop\nand forestry products, animal products")
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "tot_productivity_pers",
          title = "Total productivity per person\ncrops, animals, crop\nand forestry products, animal products")
```

### Per ha

#### Overall Scatter

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "tot_productivity_ha",
    ytitle = "Total productivity per ha\ncrops, animals, crop\nand forestry products, animal products",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### By Region

```{r}
caet_performance_scatter(
    x = "totscore_caet",
    y = "tot_productivity_ha",
    facet = "location_level_one_name",
    ytitle = "Total productivity per ha\ncrops, animals, crop\nand forestry products, animal products",
    xtitle = "Total CAET Score",
    scale = "log10"
)
```

#### Spearman's rank Correlations

```{r}
correlations_table(indicator = "tot_productivity_ha")
```

#### Test of Mean - ProSoils vs Comparison

```{r}
mean_test(indicator = "tot_productivity_ha",
          title = "Total productivity per ha\ncrops, animals, crop\nand forestry products, animal products")
```

#### Test of Median - ProSoils vs Comparison

```{r}
median_test(indicator = "tot_productivity_ha",
          title = "Total productivity per ha\ncrops, animals, crop\nand forestry products, animal products")
```